\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-06-05 trunk/concepts.tex
updates

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.4]{figs/flexible-timelines.pdf}
\caption{\small Tokens with flexible temporal intervals and parametric
  constraints between tokens. This example shows the triggering of a
  water sampler based on a feature threshold while the vehicle
  Yo-Yo's. The \texttt{Waypoint\_Yo-Yo} token has a flexible duration,
  start \& end times.}
\label{fig:flex-timelines}
\end{figure}

@@

  \begin{figure}[t]
    \centering 
    \subfloat[\small Timelines representing initial state
    and goals for a Shopping Agent.]{\label{fig:europapr1}\includegraphics[scale=0.4]{figs/europa-pr-1.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial state.]{\label{fig:europapr:merge}\includegraphics[scale=0.4]{figs/europa-pr-merge.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to own
    a drill by time $10$ by activating corresponding
    token.]{\label{fig:europapr:activate}\includegraphics[scale=0.4]{figs/europa-pr-activate.pdf}} 
    \caption{\small Evolution of a timeline from the Shopping Agent example.}
  \end{figure}

@@

\begin{figure} \centering
  \includegraphics[scale=0.45]{figs/europa-pr-states.jpg}
  \caption{\small Possible transitions for a token state.}
\label{fig:europapr:states}
\end{figure}

@@

  \begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/europa-pr-rules.pdf}
    \caption{\small Master and Slave tokens generated as a result of a domain rule.}
    \label{fig:europapr:rules}
  \end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[scale=2.3]{figs/flexible-timelines.jpeg}
\caption{\small Tokens with flexible temporal intervals and parametric
  constraints between tokens. This example shows the triggering of a
  water sampler based on a feature threshold while the vehicle
  Yo-Yo's. The \texttt{Waypoint\_Yo-Yo} token has a flexible duration,
  start \& end times.}
\label{fig:flex-timelines}
\end{figure}

@@

  \begin{figure}[t]
    \centering 
    \subfloat[\small Timelines representing initial state
    and goals for a Shopping Agent.]{\label{fig:europapr1}\includegraphics[scale=2.2]{figs/europa-pr-1.jpeg}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial state.]{\label{fig:europapr:merge}\includegraphics[scale=2.2]{figs/europa-pr-merge.jpeg}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to own
    a drill by time $10$ by activating corresponding
    token.]{\label{fig:europapr:activate}\includegraphics[scale=2.2]{figs/europa-pr-activate.jpeg}} 
    \caption{\small Evolution of a timeline from the Shopping Agent example.}
  \end{figure}

@@

\begin{figure} \centering
  \includegraphics[scale=3.9]{figs/europa-pr-states.jpeg}
  \caption{\small Possible transitions for a token state.}
\label{fig:europapr:states}
\end{figure}

@@

  \begin{figure}[t]
    \centering
    \includegraphics[scale=2.5]{figs/europa-pr-rules.jpeg}
    \caption{\small Master and Slave tokens generated as a result of a domain rule.}
    \label{fig:europapr:rules}
  \end{figure}

### 2012-06-05 trunk/results.tex
updates

\begin{figure}[htpb]
\centering
\includegraphics[width=0.35\textwidth]{figs/gulper.jpg}
\caption{\small{The Gulper water sampler \cite{Bird07} on MBARI's
    upper water-column Dorado AUV.}}
\label{fig:gulper}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[scale=0.65]{figs/inl.jpg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission \kcomment{using a scripted mission plan} in the Monterey
  Bay in August 2005. It shows the location of the AUV transect in the
  bay (left) and optical backscatter image at the 420 Nm frequency
  showing the INLs patchy nature (right). \emph{Image courtesy: John
    Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=0.8\textwidth]{figs/front-mi.jpg}
\caption{\small{Survey trackline of AUV following a thermal
    gradient. Image in the middle shows the temperature while the
    bottom figure shows different phases in the algorithm.}}
\label{fig:mi-front}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.pdf}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.45\textwidth]{figs/june11-drifter-follow-180-181.pdf}
\caption{\small{A June 2011 drifter cruise shown in the Earth
    frame. Deviations in the AUV transect are based on the frame of
    reference in addition to positional errors \cite{das11b}.}}
\label{fig:drifter-errors}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:sep10-ship}\includegraphics[width=0.44\textwidth]{figs/sep10-canon-cruise.png}}
\subfloat[]{\label{fig:sep10-transects}\includegraphics[width=0.40\textwidth]{figs/september-iterations.pdf}}
  \caption{\small{The offshore \can ESP-drifter following cruise
      \cite{das11b}. Fig. \ref{fig:sep10-ship} shows the ESP drifter
      foreground with the R/V \emph{Western Flyer} with the image
      taken from the R/V \emph{Zephyr}. Fig \ref{fig:sep10-transects}
      shows the 86 km transect of the Dorado following the ESP drifter
      about 100 Nm from California shores.}}
\label{fig:gulper}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of a
  separate AUV platform. {\color{yellow}Yellow} dots show the track
  line of a GPS-enabled drifter used for seeding the experiment over
  the Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
\centering 
\subfloat[Temperature]{\label{fig:sep11-temp}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-temp.png}} 
\subfloat[Salinity]{\label{fig:sep11-sal}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-salinity.png}}\\
\subfloat[Fluorescence line height]{\label{fig:sep11-flh}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-flh.png}} 
\subfloat[Nitrate]{\label{fig:sep11-n2}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-n2.png}} 
\caption{\small Interpolated results of a September 2011 \rx mission
  in the Monterey Bay with the profiling \texttt{Wirewalker}
  \cite{rainville01,pinkel11} instrument. Plots show the instrument
  was entrained between two fronts. \emph{Image courtesy: Rishi
    Graham, MBARI}}
  \label{fig:sept11-wirewalker}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od and how it fits into \can
  field experiments]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
  \subfloat[Current implementation of \od for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.325\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.37\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.325\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with
  the \od in use. Fig. \ref{fig:odss-virtual} shows a drifter tracking
  tool used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. Fig. \ref{fig:odss-ipad} shows \od use on an iPad.}
\label{fig:odss2}
\end{figure*}

@@

Operationally, the \od has become a software system that the scientist
consults during a \can field campaign. S/he consults up-to-date model
outputs, synoptic views of ocean color from remote sensing data and
weather conditions for the next $24$-hour planning cycle and then
queries the system to compute candidate sampling locations. In the
near future, the \od will consult its situational awareness database,
incorporate model outputs projecting these outputs into the space-time
region of interest to generate candidate hypotheses with associated
utility metrics. With the scientist's guidance the automated planner
would then determine the most viable robotic option(s) to be
dispatched (underwater, surface or aerial), given available resources,
distance of travel, required payload and the environment. For
instance, gliders could be chosen for longer-duration missions with
smaller payload requirements in areas of moderate to weak ocean
currents. The automated planner would balance these criteria to
compute a viable trajectory plan for the selected vehicle. Vehicles
with more controllability would be given a specified area to survey
and the path generated \situ. Goals are communicated to the robot
after analysis on shore for selective targeting of features by the
conglomerate of vehicles in the ocean \kcomment{that are} being
tracked by the \od. \kcomment{To date}, the \od has provided a simple
yet functional tool for scientists to use in the daily complex
decision making and the following experiment and survey design
needs. It has helped train scientists to think of expanding their
repertoire of tools for the scientific process and in the process it
enabled a mixed team of engineers and scientists to interact at the
functional level of the systems' capabilities.

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[width=0.45\textwidth]{figs/gulper.jpeg}
\caption{\small{The Gulper water sampler \cite{Bird07} on MBARI's
    upper water-column Dorado AUV.}}
\label{fig:gulper}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[scale=0.65]{figs/inl.jpeg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission \kcomment{using a scripted mission plan} in the Monterey
  Bay in August 2005. It shows the location of the AUV transect in the
  bay (left) and optical backscatter image at the 420 Nm frequency
  showing the INLs patchy nature (right). \emph{Image courtesy: John
    Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=0.8\textwidth]{figs/front-mi.jpeg}
\caption{\small{Survey trackline of AUV following a thermal
    gradient. Image in the middle shows the temperature while the
    bottom figure shows different phases in the algorithm.}}
\label{fig:mi-front}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.jpeg}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.45\textwidth]{figs/june11-drifter-follow-180-181.jpeg}
\caption{\small{A June 2011 drifter cruise shown in the Earth
    frame. Deviations in the AUV transect are based on the frame of
    reference in addition to positional errors \cite{das11b}.}}
\label{fig:drifter-errors}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:sep10-ship}\includegraphics[width=0.44\textwidth]{figs/sep10-canon-cruise.jpeg}}
\subfloat[]{\label{fig:sep10-transects}\includegraphics[width=0.41\textwidth]{figs/september-iterations.jpeg}}
  \caption{\small{The offshore \can ESP-drifter following cruise
      \cite{das11b}. Fig. \ref{fig:sep10-ship} shows the ESP drifter
      foreground with the R/V \emph{Western Flyer} with the image
      taken from the R/V \emph{Zephyr}. Fig \ref{fig:sep10-transects}
      shows the 86 km transect of the Dorado following the ESP drifter
      about 100 Nm from California shores.}}
\label{fig:gulper}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.jpeg}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of a
  separate AUV platform. {\color{yellow}Yellow} dots show the track
  line of a GPS-enabled drifter used for seeding the experiment over
  the Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
\centering 
\subfloat[\small Temperature]{\label{fig:sep11-temp}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-temp.jpeg}} 
\subfloat[\small Salinity]{\label{fig:sep11-sal}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-salinity.jpeg}}\\
\subfloat[\small Fluorescence line height]{\label{fig:sep11-flh}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-flh.jpeg}} 
\subfloat[\small Nitrate]{\label{fig:sep11-n2}\includegraphics[width=0.5\textwidth]{figs/sep11-ww-n2.jpeg}} 
\caption{\small Interpolated results of a September 2011 \rx mission
  in the Monterey Bay with the profiling \texttt{Wirewalker}
  \cite{rainville01,pinkel11} instrument. Plots show the instrument
  was entrained between two fronts. \emph{Image courtesy: Rishi
    Graham, MBARI}}
  \label{fig:sept11-wirewalker}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od and how it fits into \can
  field experiments]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.jpeg}}\\
  \subfloat[Current implementation of \od for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.jpeg}}
\caption{\small The Oceanographic Decision Support System (\ode) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.325\textwidth]{figs/october-canon-meeting.jpeg}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.37\textwidth]{figs/virtual-drifter-tool.jpeg}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.325\textwidth]{figs/photo-ipad-2.jpeg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with
  the \od in use. Fig. \ref{fig:odss-virtual} shows a drifter tracking
  tool used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. Fig. \ref{fig:odss-ipad} shows \od use on an iPad.}
\label{fig:odss2}
\end{figure*}

@@

Operationally, the \od has become a software system that the scientist
consults during a \can field campaign. S/he consults up-to-date model
outputs, synoptic views of ocean color from remote sensing data and
weather conditions for the next $24$-hour planning cycle and then
queries the system to compute candidate sampling locations. In the
near future, the \od will consult its situational awareness database,
incorporate model outputs projecting these outputs into the space-time
region of interest to generate candidate hypotheses with associated
utility metrics. With the scientist's guidance the automated planner
would then determine the most viable robotic option(s) to be
dispatched (underwater, surface or aerial), given available resources,
distance of travel, required payload and the environment. For
instance, gliders could be chosen for longer-duration missions with
smaller payload requirements in areas of moderate to weak ocean
currents. The automated planner would balance these criteria to
compute a viable trajectory plan for the selected vehicle. Vehicles
with more controllability would be given a specified area to survey
and the path generated \situ. Goals are communicated to the robot
after analysis on shore for selective targeting of features by the
conglomerate of vehicles in the ocean \kcomment{that are} being
tracked by the \ode. \kcomment{To date}, the \od has provided a simple
yet functional tool for scientists to use in the daily complex
decision making and the following experiment and survey design
needs. It has helped train scientists to think of expanding their
repertoire of tools for the scientific process and in the process it
enabled a mixed team of engineers and scientists to interact at the
functional level of the systems' capabilities.
